---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# xplrrr

<!-- badges: start -->
<!-- badges: end -->

This package makes explatory data analysis (EDA) simple and seamless. EDA is a crucial phase in the data science workflow as it allows us get a fist glimpse of the data. It is important to identify statistical characteristics of the data so that we can properly set up the rest of the analysis.

## Installation

You can install the released version of xplrrr from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("xplrrr")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("UBC-MDS/xplrrr")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(xplrrr)
## basic example code
```


