---
title: "Using xplrrr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{xplrrr-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE,
                      # collapse = TRUE,
                      # comment = "#>",
                      dpi = 480)
```

`xplrrr` aims to simplify data exploration with R in four aspects:

- feature correlation visualization
- data summary
- outliers detection 
- missing data

The package was developed as part of UBC MDS course.

First, start with loading the library

```{r setup}
library(xplrrr)
library(dplyr)
```

In this vignette we will be working with the `iris` dataset.

At first, let's visualize our features and their pairwise correlations and distributions:

```{r eplore_feature_map}
explore_feature_map(iris)
```

Now let's explore summary statistics:

```{r eplore_summary}
explore_summary(iris)
```

Let's see if there are any outliers:

```{r eplore_outliers}
explore_outliers(iris %>% select('Sepal.Length', 'Sepal.Width', 'Petal.Length', 'Petal.Width'), 2)
```

Finally, lets test see if `airquality` dataset has any missing data:

```{r explore_missing}
explore_missing(airquality)
```
